---
title: "Statistical Inference Course Project Part 2"
author: "yhuai"
date: "2018/4/21"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
## Part 2: Basic Inferential Data Analysis Instructions

Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

```{r echo=FALSE}
library(datasets)
library(ggplot2)

data("ToothGrowth")
data <- ToothGrowth
str(data)
summary(data)
```


From the summary function and the plot, we can find that the tooth growth length is increasing as dosage increasing. The two kind of supplements-OJ and VC, looks have similar effects when dosage is 2.
```{r}
g <- ggplot(data=ToothGrowth,aes(x=factor(dose), y=len))
g <- g + facet_grid(.~ data$supp)
g <- g + geom_boxplot(aes(fill=supp))
g <- g + labs(x="Dose",y="length",title="Tooth Length by Dose Based on Types")
g

```


Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

We assume that OJ and VC have the same effect on tooth growth.

```{r}
#Hypothesis
h1 <- t.test(len ~ supp, data=subset(data,dose==0.5))
h1
p1 <- h1$p.value
h2 <- t.test(len ~ supp, data=subset(data,dose==1.0))
h2
p2 <- h2$p.value
h3 <- t.test(len ~ supp, data=subset(data,dose==2.0))
h3
p3 <- h3$p.value
rp1 <- round(p1,3)
rp2 <- round(p2,3)
rp3 <- round(p3,3)
ma <- matrix(c(rp1,rp2,rp3),ncol=3,byrow = TRUE)
colnames(ma) <- c("test1","test2","test3")
rownames(ma) <- c("p-value")
ma <- as.table(ma)
ma
```

## Conclustions
As the hypothesis part show, the confidence interval is 95%, and only when the dosage is 2, the p-value is greater than 0.05 threshold. 

So we can say,  the OJ have better performance in dosage 0.5 and 1.0, OJ and VC have the same effect only when dosage is 2.0
