---
title: "Statistical Inference Course Project Part 1"
author: "yhuai"
date: "2018/4/21"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
## Overview
This is the Coursera Johns Hopkins University Data Science Specialization -- Statistical Inference Course Project

The project consists of two parts:

1.A simulation exercise.
2.Basic inferential data analysis.

##Part 1: Simulation Exercise Instructions

In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.


```{r}
set.seed(19930319)
lambda <- 0.2; n <- 40;
means = NULL
for (i in 1:1000) means = c(means, mean(rexp(n,lambda)))
hist(means,breaks=50,xlim=c(2,8))

mean(means)
abline(v=mean(means),col="red",lwd="2")

```



Show the sample mean and compare it to the theoretical mean of the distribution.
```{r}
a1 <- lambda^-1
theoretical_mean <- a1
b1 <- mean(means)
sample_mean <- b1
table(theoretical_mean,sample_mean)

```



Show how variable it is and compare it to the theoretical variance of the distribution.
```{r}
a2 <- (1/lambda)^2/n
theoretical_var <- a2
b2 <- var(means)
sample_var <- b2
table(theoretical_var,sample_var)

```




Based on Central Limit Theorem, our number of smaples is big(1000), the simulated exponential distribution is close to normal distribution.
```{r}
x <- seq(2,8,length=2*n)
y <- dnorm(x,mean(means),sd(means))
plot(x,y,type = "l",col="red")



dataset <- matrix(rexp(n*1000,lambda),1000)
RowMeans <- apply(dataset, 1, mean)
df <- data.frame(RowMeans)

g <- ggplot(df,aes(x=RowMeans))
g <- g + geom_histogram(bins=50,binwidth = lambda,color="yellow",aes(y=..density..))
g <- g + geom_vline(xintercept = sample_mean,size=1.0,color="red")
g <- g + stat_function(fun = dnorm,args=list(mean=sample_mean,sd=sample_var),color="blue",size=1)
g <- g + stat_function(fun = dnorm,args=list(mean=theoretical_mean,sd=theoretical_var),color="pink",size=1)
g
```





