---
title: "R Markdown Presentation & Plotly"
author: "yhuai"
date: "24 May 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Description

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Slide with Plotly1

```{r, echo=TRUE, comment=NA, cache=FALSE, message=FALSE, warning=FALSE}
library(plotly)
datasets::mtcars
plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode = "markers")
plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode = "markers", color = as.factor(mtcars$cyl))
plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode = "markers", color = mtcars$disp)
plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode = "markers", color = as.factor(mtcars$cyl),size=mtcars$hp)

```

## Slide with Plotly2

```{r, echo=TRUE, comment=NA, cache=FALSE, message=FALSE, warning=FALSE}
library(plotly)
set.seed(1993)
temp <- rnorm(100, mean=30, sd=5)
pressue <- rnorm(100)
dtime <- 1:100
plot_ly(x = temp, y = pressue, z = dtime,
        type = "scatter3d", mode="markers", color=temp)

data("airmiles")
airmiles
plot_ly(x=time(airmiles), y=airmiles)

```

## Slide with Plotly3

```{r, echo=TRUE, comment=NA, cache=FALSE, message=FALSE, warning=FALSE}
library(plotly);library(tidyr);library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
    gather(index,price) %>%
    mutate(time=rep(time(EuStockMarkets),4))

plot_ly(stocks, x = stocks$time, y = stocks$price, color=stocks$index)

plot_ly(iris, x = iris$Petal.Length, type="histogram" )
plot_ly(iris, y = iris$Petal.Length, color = iris$Species, type="box" )

terrain1 <- matrix(rnorm(100*100), nrow = 100, ncol=100)
plot_ly(z=terrain1, type="heatmap")

terrain2 <- matrix(sort(rnorm(100*100)), nrow = 100, ncol=100)
plot_ly(z=terrain2, type="surface")
```
